### 2015-09-29 untitled.tex
edited untitled.tex

Let's now look at the computation segment $C_2^2$ of the second job of task $\tau_2$. This segment is placed back to the ready queue at time $19$ after its self-suspension. Without period enforcer, this computation segment should be executed from $19$ to $20$. However, the period enforcer algorithm intentionally defers this computation segment to ensure \emph{the periodic demand} of the computation segment $C_2^2$. Therefore, this computation segment is \emph{activated} to the ready queue at time $9+T_2=9+11=20$. This results in a deadline miss.\footnote{By using the notations of \cite{Raj:suspension1991}, $ET_{2,1}^2=9, ET_{2,2}^2 = \max\{9+11, 19\}=20$.}

>>>>

Let's now look at the computation segment $C_2^2$ of the second job of task $\tau_2$. This segment is placed back to the ready queue at time $19$ after its self-suspension. Without period enforcer, this computation segment should be executed from $19$ to $20$. However, the period enforcer algorithm intentionally defers this computation segment to ensure \emph{the periodic demand} of the computation segment $C_2^2$. Therefore, this computation segment is \emph{activated} to the ready queue at time $9+T_2=9+11=20$. This results in a deadline miss.\footnote{By using the notations in \cite{Raj:suspension1991}, we have $ET_{2,1}^2=9, ET_{2,2}^2 = \max\{9+11, 19\}=20$. The superscript $^2$ is for denoting the second computation segment of task $\tau_2$.}
